Download, Compile and Link OpenBLAS Library with R

### 2021-03-31 README.Rmd
Update README.md. Add DOI of the paper.

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  |
  |
  |
  | **Summary**
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
output: 
  bookdown::github_document2:
    number_sections: true
    toc: true
    toc_depth: 2
toccolor: 'blue'
editor_options: 
  markdown: 
    wrap: 72
---

**ropenblas**

[![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![total](http://cranlogs.r-pkg.org/badges/grand-total/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![month](https://cranlogs.r-pkg.org/badges/ropenblas)](https://CRAN.R-project.org/package=ropenblas)

>>>>

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  |
  |
  |
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  | **Summary**
output: 
  bookdown::github_document2:
    number_sections: false
    toc: true
    toc_depth: 2
toccolor: 'blue'
editor_options: 
  markdown: 
    wrap: 72
---

**ropenblas package**

[![DOI](https://joss.theoj.org/papers/10.21105/joss.02769/status.svg)](https://doi.org/10.21105/joss.02769)
[![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![total](http://cranlogs.r-pkg.org/badges/grand-total/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![month](https://cranlogs.r-pkg.org/badges/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
